Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-03 manuscript-chicago.Rmd
Format quotes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

This skepticism can be summarized in a quote by Lisa Anderson:

> The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts. [@anderson2011demystifying]

@@

>I know that I have been away from the media for a long time, and I have missed
having direct contact with the citizens, but I have always been following up
with the daily occurrences and gathering the information so that my speech can
be built on what is said by the street.

\noindent With few exceptions, Assad chose to keep social media platforms up and running.
Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
of social protest online and in the streets by shutting down the Internet.
During these times, however, she finds that military repression increases.
However, government information about the citizens decreases; as such, many
regimes have elected to maintain Internet connectivity as a means of monitoring
and surveilling their citizens.

>>>>

documentclass     : "apa6"
classoption       : "man"
header-includes   :
  - "\\usepackage{setspace}"
output            : papaja::apa6_pdf
---

@@

This skepticism can be summarized in a quote by Lisa @anderson2011demystifying:

\begin{singlespace}
\setlength{\leftskip}{1cm}

\noindent The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts.

\setlength{\leftskip}{0pt}
\end{singlespace}

@@

\begin{singlespace}
\setlength{\leftskip}{1cm}

\noindent I know that I have been away from the media for a long time, and I have missed
having direct contact with the citizens, but I have always been following up
with the daily occurrences and gathering the information so that my speech can
be built on what is said by the street.

\setlength{\leftskip}{0pt}
\end{singlespace}
\noindent With few exceptions, Assad chose to keep social media platforms up and running.
Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
of social protest online and in the streets by shutting down the Internet.
During these times, however, she finds that military repression increases.
However, government information about the citizens decreases; as such, many
regimes have elected to maintain Internet connectivity as a means of monitoring
and surveilling their citizens.
